Parameter estimation

### 2023-03-08 SFE-article/Article_Model_Parameters.tex
08.03

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase is a function of distance. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
The collected dataset, obtained from the extraction of caraway seeds at different operating conditions, is used to estimate unknown parameters. The model-based parameter estimation applies the maximum likelihood method to estimate values of the extraction kinetic parameters such as mass partition factor, internal diffusion coefficient and radial diffusion.

@@

\section{Introduction}
%\subfile{Sections/introduction}

%\section{Materials and methods} \label{CH: Materials and methods}

\section{$CO_2$ properties} \label{CH: Thermodynamic}
%\subfile{Sections/Thermo}

\clearpage
%\subfile{Sections/Materials_and_methods}

@@

{\footnotesize
\begin{equation}
\begin{align}
        \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \\
        \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)   
    \end{align}    
\end{equation}
\label{EQ: CompressibleEuler}
}

@@

\subsection{Extraction model} \label{CH: Extraction_model}
%\subfile{Sections/Model}

@@

\subsection{Parameter estimation} \label{CH: Parameter_estimation}
%\subfile{Sections/Parameter_estimation}

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Governing equations}
%\subfile{Sections/Gouverning_equation_derivation}

\subsection{Bayes theorem} \label{CH: Bayes}
%\subfile{Sections/Bayes_Theorem}

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase is a function of distance. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent. The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient and saturation concentration are obtained from parameter estimation. The parameters are estimated based on four experiments performed at $40^\circ C$ and $50^\circ C$ at $200$ bar and $300$ bar. The model-based parameter estimation uses the maximum likelihood estimation under assumption of normal error given for yield data.

@@

\section{Introduction}
\subfile{Sections/introduction}

\section{Materials and methods} \label{CH: Materials and methods}

\subsection{Supercritical fluids} \label{CH: Thermodynamic}
\subfile{Sections/Thermo}

%\clearpage
%\subfile{Sections/Materials_and_methods}

@@

{\footnotesize
\begin{align}
        \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \\
        \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)   
    \end{align}  
\label{EQ: CompressibleEuler}
}

@@

\subsection{Extraction model} \label{CH: Extraction_model}
\subfile{Sections/Model}

@@

\subsection{Parameter estimation} \label{CH: Parameter_estimation}
\subfile{Sections/Parameter_estimation}

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Governing equations}
\subfile{Sections/Gouverning_equation_derivation}

\subsection{Bayes theorem} \label{CH: Bayes}
\subfile{Sections/Bayes_Theorem}

### 2023-03-08 SFE-article/Sections/Model.tex
08.03

		The movement of the mobile pseudo-homogeneous phase (Eq. \ref{Model_fluid}) is considered only in the axial direction. The properties of the system in the radial direction is assumed to be uniform. In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist. Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction. As a result, the plug flow model can be introduced. The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time. Moreover, the pressure is considered to be constant along the fixed bed. The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.

@@

		The heat balance (Eq. \ref{Model_heat}) consists of the convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. We consider no heat loss through the wall, and there is no heat generation in the system. Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.

@@

	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
	The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.

@@

	where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively. ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term. ${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{magenta}A}$ is the extractor’s cross section, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.

@@

			\subsubsection{Kinetic term} \label{CH: Kinetic}
			As the solvent flows through the bed, \sout{it forms a film around the porous solid particle and occupies its pores.} {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions. Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected. In this work, the molecular diffusion is assumed.}. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}. The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$. At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore. The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$. It can be assumed that the two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.

@@

			\sout{The kinetic term, denoted as equation \ref{Model_kinetic_basic}, corresponds to a solute transfer rate between both phases. This term is made of the overall diffusion coefficient and the concentration gradient (between one phase and its equilibrium concentration), which acts as a driving force for the process.} {\color{blue}The mass transfer kinetic (Eq. \ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent. The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as

@@

			Equation \ref{Model_kinetic} is the full representation of the kinetic term.

			{\footnotesize
				\begin{align}
					\label{Model_kinetic}
					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
			\end{align} }

@@

@@

			The efficiency of the process (the yield) is calculated according to one of Eq. \ref{Model_measurment}, which evaluates the mass of solute at the exit of the extraction unit and sums it. The integral form of the measurement equation can be transformed into the differential form, and augmented with model equations to be solved simultaneously.

			{\footnotesize
				\begin{align} 
					\label{Model_measurment}
					y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
					y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
					\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
					\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
			\end{align}	}

>>>>

	The movement of the mobile pseudo-homogeneous phase (Eq. \ref{Model_fluid}) is considered only in the axial direction. The properties of the system in the radial direction is assumed to be uniform. In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist. Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction. As a result, the plug flow model can be introduced. The particle size distribution and the void fraction of the solid phase cab change along an extractor but they remain constant in time. Moreover, the thermodynamic pressure is considered to be constant along the device, as discussed above. The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.

@@

    {\color{red}
	The heat balance (Eq. \ref{Model_heat}) consists of the convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. We consider no heat loss through the wall, and there is no heat generation in the system. Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream %$T_{In}(t)$.

@@

	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
	The detail derivation of the mass balance equation for the fluid phase can be found in the appendix ({\color{red}REF}). The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.

@@

	where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively. ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term. ${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient and $u$ is the superficial velocity.

@@

	\subsubsection{Kinetic term} \label{CH: Kinetic}
	As the solvent flows through the bed, {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions. Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected}. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}. The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$. At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore. The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$. It can be assumed that the two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.

@@

		{\color{blue}The mass transfer kinetic (Eq. \ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent. The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as

@@

			Equation \ref{Model_kinetic_no_sat} is the full representation of the kinetic term.

			{\footnotesize
				\begin{align}
					\label{Model_kinetic_no_sat}
					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
			\end{align} }

        The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\Gamma(c_f)$ (equation \ref{EQ: C_sat_function}). $\Gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.

        {\footnotesize
            \begin{equation}
                \Gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
                \label{EQ: C_sat_function}
            \end{equation}
        }

        where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$.

        The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}

        {\footnotesize
			\begin{align}
				\label{Model_kinetic}
				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} } \Gamma(c_f) \left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
		\end{align} }

@@

        {\color{blue} The heat equation was introduced in the previous chapter. The heat balance describe movement of the internal energy in the system. For real gases it is complicated to write the heat balance in terms of temperature. Alternatively, the temperature can be obtained based on the equation of state if the internal energy and pressure are know. A roootfinder can be used to find a value of temperature, which satisfy the equation of state given values of internal energy and pressure. The temperature needs to be reconstructed from the internal energy in every time-step.
		}

@@

		The efficiency of the process (the yield) is calculated according to equations \ref{Model_measurment_1} to \ref{Model_measurment_2}, which evaluate the mass of solute at the exit of the extraction unit and sums it. The integral form of the measurement equation can be transformed into the differential form, and augmented with model equations to be solved simultaneously.

		{\footnotesize
			\begin{align} 
				\label{Model_measurment_1}
				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
                \label{Model_measurment_2}
		\end{align}	}

### 2023-03-08 SFE-article/Sections/Thermo.tex
08.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

@@

		\begin{figure*}[h!]
			\begin{subfigure}[b]{\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
				\caption{The compressibility factor based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_Compressibility}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
				\caption{The fluid density based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_Density}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
				\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_CP}
			\end{subfigure}
			\caption{Properties of $CO_2$ based on the equation of state}
			\label{fig: SFE_Properties}
		\end{figure*}

@@

        \begin{figure*}[h!]
			\centering
			\includegraphics[trim = 1.5cm 4.0cm 1.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
			\caption{Viscosity obtained based on different correlations}
            \label{fig: SFE_Properties_mu}
		\end{figure*}

@@

        \begin{figure*}[h!]
			\centering
			\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity obtained based on different correlations}
            \label{fig: SFE_Properties_kt}
		\end{figure*}

>>>>

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

    A supercritical fluid (SCF) is any substance at a temperature and pressure above its critical point, where distinct liquid and gas phases do not exist, but below the pressure required to compress it into a solid. It can effuse through porous solids like a gas, overcoming the mass transfer limitations that slow liquid transport through such materials. SCF are much superior to gases in their ability to dissolve materials like liquids or solids. Also, near the critical point, small changes in pressure or temperature result in large changes in density, allowing many properties of a supercritical fluid to be "fine-tuned". By changing the pressure and temperature of the fluid, the properties can be "tuned" to be more liquid-like or more gas-like.

@@

		\begin{figure*}[H]
			\begin{subfigure}[b]{0.95\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
				\caption{The compressibility factor based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_Compressibility}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{0.95\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
				\caption{The fluid density based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_Density}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{0.95\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
				\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_CP}
			\end{subfigure}
			\caption{Properties of $CO_2$ based on the equation of state}
			\label{fig: SFE_Properties}
		\end{figure*}

@@

        \begin{figure*}[H]
			\centering
			\includegraphics[trim = 1.5cm 4.0cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
			\caption{Viscosity obtained based on different correlations}
            \label{fig: SFE_Properties_mu}
		\end{figure*}

@@

        \begin{figure*}[H]
			\centering
			\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity obtained based on different correlations}
            \label{fig: SFE_Properties_kt}
		\end{figure*}

### 2023-03-08 SFE-article/Sections/introduction.tex
08.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	%{\color{brown}Intro about extraction}\\
	The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years. Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and {\color{blue} both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity). Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties. The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids. The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.}

	%{\color{brown} Literature review of the models}\\
	\sout{The supercritical extraction process is considered unconventional due to the lack of formulation of one general model, properties that strongly depend on working conditions and its unsteady nature. Understanding the physics behind the phenomena and the proper mathematical description is necessary to predict the process outcome. Several extraction models have been developed to characterize different mass transfer mechanisms and equilibrium relationships.}
	{\color{blue}The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}. The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit. Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships}.

@@

	Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to {\color{blue} a process in which a hot ball is cooled in a uniform medium} \sout{the process of cooling down a hot ball in a uniform medium}. {\color{blue}The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor. }

	\citet{Sovova1994} \sout{presented the Broken-and-Intact Cell model, which assumes the presence of two solid phases, the broken and intact cells. The results of applying Sovova's model allow distinguishing three phases of the extraction process (constant extraction rate, falling extraction rate, and diffusion-controlled periods) directly at the modelling stage.}
	{\color{blue} presented the Broken-and-Intact Cell model. The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted. The solute from the broken cells is easily accessible for the solvent. The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
		However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells. This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
		In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.}

@@

	%{\color{brown} Summary of the manuscript}\\
	\sout{In this work, the process model represents supercritical extraction and consists of a set partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables. The process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.The impact of mass flow rate, pressure, and inlet temperature on the model's output is analyzed. In this work, the sensitivity analysis results are used to prove if the considered variables affect the extraction process and can be used as decision variables in optimization problems. The novelty is the application of the local sensitivity analysis in the case of supercritical extraction.}
	{\color{blue}In this work, a distributed-parameter model, based on \citet{Reverchon1996} and \citet{Vargas2006}, is used to describe a fluid-solid extraction process of 'carqueja' oil from 'Baccharis Trimera' leaves with $CO_2$ as a solvent. The process model consists of three partial differential equations: two mass balance equations and one heat balance equation. To enhance understanding of the process model, the local sensitivity analysis is used to investigate the effect of parameters on the model's output. The presented sensitivity analysis results are restricted to parameters related to operating conditions only. Furthermore, the sensitivity analysis is used to prove which of the analysed variables can be used as decision variables in optimisation problems.}

>>>>

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	%{\color{brown}Intro about extraction}\\
	The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years. Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity). Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties. The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids. The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.

	%{\color{brown} Literature review of the models}\\
	The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}. The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit. Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships.

	Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to a process in which a hot ball is cooled in a uniform medium. The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor.

	\citet{Sovova1994} presented the Broken-and-Intact Cell model. The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted. The solute from the broken cells is easily accessible for the solvent. The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent. However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells. This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.

@@

    \iffalse

    In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.

@@

    \fi

	In our model, the extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel. The solvent is firstly brought to super-critical condition, pumped through a fixed-bed, of finely chopped biomass, where the solute is extracted from the biomass. Then, the solvent and solute from the extractor are separated in a flush drum, and the extract is collected. The flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor’s feed can be measured and manipulated. The pressure ($P$) in the vessel can be measured and manipulated, while the outlet temperature ($T_{out}$) can only be measured. A simplified flow diagram is depicted in Figure \ref{fig: SFE_drawing} .

    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.95\columnwidth]{SFE-article/Figures/SFE_PFD_cropped.pdf}
        \caption{Process flow diagram}
        \label{fig: SFE_drawing}
    \end{figure}
